Apparent preferences for cognitive effort fade when multiple forms of effort and delay are interleaved in a foraging environment

### 2020-03-16 Cost_manuscript.Rmd
loading done, suppressing unncesessary warning messages

# load data
dataBtw <- tibble(SubjID = files) %>%
  mutate(contents = map(SubjID, ~ read_csv(., col_types = cols())))  %>%
  mutate(Cost = substring(SubjID, 5, 8),
         Cost = case_when(Cost == "wait" ~ "Wait",
                          Cost == "cogT" ~ "Cognitive",
                          Cost == "phys" ~ "Physical",
                          Cost == "phea" ~ "Easy"),
         SubjID = as.integer(substring(SubjID, 0, 3))) %>%
  unnest() %>%
  mutate(rawChoice = Choice, 
         RT = ifelse(RT > 14.1, 14, RT),
         Choice = ifelse(Choice == 2, 1, Choice), # forced travels (2) become acceptances (1)
         Half = ifelse(Block < 4, "Half_1", "Half_2"),
         Cost = factor(Cost, levels = c("Physical", "Cognitive", "Wait", "Easy")),
         optimal = case_when(
          (Handling == 10 & Offer < 8) ~ 0,
          (Handling == 14 & Offer < 20) ~ 0,
          TRUE ~ 1
          )
         )

# get a simple subject list and the number of subjects
subjList_btw <- unique(dataAll$SubjID)
nSubjs_btw <- length(subjList)

@@

# load the data and remove extreme subjects
dataWth <- data_frame(SubjID = files) %>% 
  mutate(contents = map(SubjID, ~ read_csv(., col_types = cols())))  %>%
  mutate(SubjID = substring(SubjID, 0, 3)) %>%
  unnest() %>%
  mutate(RT = ifelse(RT > 10.1, 10, RT),
         Half = ifelse(Block < 4, "Half_1", "Half_2"),
         Btype = BlockType) %>%
  unite(Cost, Cost, BlockType) %>%
  mutate(rawChoice = Choice,
         Choice = ifelse(Choice == 2, 1, Choice),
         Cost = case_when(Cost == "WAIT_0" ~ "Wait_C",
                           Cost == "COGNITIVE_0" ~ "Cognitive",
                           Cost == "GRIP_1" ~ "Physical",
                           Cost == "WAIT_1" ~ "Wait_P")) %>%
  group_by(SubjID) %>%
  mutate(BlockOrder = ifelse(Btype[1] == 0, "Cognitive1st", "Physical1st"))

# Get just the subject list and number of subjects
subjList_wth <- unique(data$SubjID)
nSubjs_wth <- length(subjList)
```

>>>>

# load data
dataBtw <- tibble(SubjID = files) %>%
  mutate(contents = map(SubjID, ~ suppressWarnings(read_csv(., col_types = cols()))))  %>%
  mutate(Cost = substring(SubjID, 5, 8),
         Cost = case_when(Cost == "wait" ~ "Wait",
                          Cost == "cogT" ~ "Cognitive",
                          Cost == "phys" ~ "Physical",
                          Cost == "phea" ~ "Easy"),
         SubjID = as.integer(substring(SubjID, 0, 3))) %>%
  unnest() %>%
  rename(TrialN = X1) %>%
  mutate(rawChoice = Choice, 
         RT = ifelse(RT > 14.1, 14, RT),
         Choice = ifelse(Choice == 2, 1, Choice), # forced travels (2) become acceptances (1)
         Half = ifelse(Block < 4, "Half_1", "Half_2"),
         Cost = factor(Cost, levels = c("Physical", "Cognitive", "Wait", "Easy")),
         optimal = case_when(
          (Handling == 10 & Offer < 8) ~ 0,
          (Handling == 14 & Offer < 20) ~ 0,
          TRUE ~ 1
          )
         )

# get a simple subject list and the number of subjects
subjList_btw <- unique(dataBtw$SubjID)
nSubjs_btw <- length(subjList_btw)

@@

# load the data and remove extreme subjects
dataWth <- data_frame(SubjID = files) %>% 
  mutate(contents = map(SubjID, ~ suppressWarnings(read_csv(., col_types = cols()))))  %>%
  mutate(SubjID = substring(SubjID, 0, 3)) %>%
  unnest() %>%
  mutate(RT = ifelse(RT > 10.1, 10, RT),
         Half = ifelse(Block < 4, "Half_1", "Half_2"),
         Btype = BlockType) %>%
  unite(Cost, Cost, BlockType) %>%
  rename(TrialN = X1) %>%
  mutate(rawChoice = Choice,
         Choice = ifelse(Choice == 2, 1, Choice),
         Cost = case_when(Cost == "WAIT_0" ~ "Wait_C",
                           Cost == "COGNITIVE_0" ~ "Cognitive",
                           Cost == "GRIP_1" ~ "Physical",
                           Cost == "WAIT_1" ~ "Wait_P")) %>%
  group_by(SubjID) %>%
  mutate(BlockOrder = ifelse(Btype[1] == 0, "Cognitive1st", "Physical1st"))

# Get just the subject list and number of subjects
subjList_wth <- unique(dataWth$SubjID)
nSubjs_wth <- length(subjList_wth)
```
